Analytic Doppler Imaging

### 2019-08-02 tex/gitlinks.tex
text

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/a5ecdb613d8739abff5e3bdf3536e894d4ec184d/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/7c3f626863f61d2a592a381e10d381862ebcb9fb/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
